\Title

### 2023-02-10 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

In a recent review paper, we reported experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2023}. These spatio-temporal motifs within the neural activity may be useful representations to perform computations for various cognitive tasks. In 1982, Abeles asked whether the role of cortical neurons is the integration of synaptic inputs or rather the detection of coincidences in temporal spiking motifs~\citep{abeles_role_1982}. While the first possibility favors the theory of rate coding, the second one emphasizes the function of temporal precision in the neural code. Since then, numerous studies have demonstrated the emergence of synchronicity of activity within a neuronal population~\citep{riehle_spike_1997, davis_spontaneous_2021}, it's use for efficient coding thanks to the use of spike latencies~\citep{perrinet_coding_2004, gollisch_rapid_2008} or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatio-temporal spiking motifs in biological spike trains. In neural models, the integration of heterogeneous delays~\citep{guise_bayesian_2014, zhang_supervised_2020, nadafian_bio-plausible_2020} allows for the efficient exploitation or detection of these spatio-temporal motifs embedded in the spike train. In particular,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a repetitive motif of spikes defined by a subset of neurons with different, but precise, relative spiking delays, i.e., the time between the arrival of an afferent spike at a given synapse and the contribution of the associated postsynaptic potential to the neuron's soma. Due to the variety of configurations and the possible coexistence of multiple superimposed motifs, this representation has a much higher information capacity than a firing rate-based approach to neural coding.

>>>>

In a recent review paper, we reported experimental evidence for the presence of precise spiking motifs embedded in recordings from biological neural tissues~\cite{grimaldi_precise_2023}. These spatio-temporal motifs within the neural activity may be useful representations to perform computations for various cognitive tasks. In 1982, Abeles asked whether the role of cortical neurons is the integration of synaptic inputs or rather the detection of coincidences in temporal spiking motifs~\citep{abeles_role_1982}. While the first possibility favors the theory of rate coding, the second one emphasizes the function of temporal precision in the neural code. Since then, numerous studies have demonstrated the emergence of synchronicity of activity within a neuronal population~\citep{riehle_spike_1997, davis_spontaneous_2021}, it's use for efficient coding thanks to the use of spike latencies~\citep{perrinet_coding_2004, gollisch_rapid_2008} or precise timing in the auditory system~\citep{deweese_binary_2002, carr_circuit_1990}. All these findings, and more~\citep{bohte_evidence_2004}, highlight the importance of the temporal aspect of the neural code and suggest the existence of spatio-temporal spiking motifs in biological spike trains. In neural models, the integration of heterogeneous delays~\citep{guise_bayesian_2014, zhang_supervised_2020, nadafian_bio-plausible_2020} allows for the efficient exploitation or detection of these spatio-temporal motifs embedded in the spike train. In particular,~\citet{izhikevich_polychronization_2006} introduced the notion of the polychronous group as a repetitive motif of spikes defined by a subset of neurons with different, but precise, relative spiking delays, i.e., the time between the arrival of an afferent spike at a given synapse and the contribution of the associated postsynaptic potential to the neuron's soma. Due to the variety of configurations and the possible coexistence of multiple superimposed motifs, this representation has a much higher information capacity than a firing rate-based approach to neural coding.
